From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
Fix paper errors

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}

@@

\author{Selcuk~Aklanoglul,
        Han~Che,
        Caroline~Dieterich,
        Marcel~Ruoff,
        Jan-Peter~Schmidt  \\
Karlsruhe Institute of Technology \\
Sebastian~Bader \\
Department Applied Informatics and  Formal Description Methods (AIFB)  \\
Karlsruhe Institute of Technology

@@

\begin{abstract}
In this study, we investigate the possibility of using Knowledge Discovery and Data Mining approaches to transform human written textual Web Application Programming Interface
(API) descriptions into structural descriptions, which
can be consumed by machines. The central vision
is to provide a solution, which ultimately allows
machines to interchange APIs with similar purposes
automatically. A use case would be to replace non-
responding data providing API (e.g. weather,
location, news) with another. Using descriptions
provided by ProgrammableWeb, with over 15000
APIs one of the most prominent public API library,
we conducted multiple steps of data cleaning and
preprocessing followed by machine learning
algorithms (K-Means, DBSCAN) to create clusters,
which we validated manually. With an average only
68,3 Words per descriptions (45,6 after
preprocessing) our results suggests, that the
needed quantity for text mining and clustering was insufficiently met. Our clusters were thus also
inconclusive.
\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{A}{pplication} Programming Interfaces (API) are not just a way to give developers access to software or services anymore. A whole business economy has established around the concept of exposing APIs in order to provide access and services. Programmable Web currently lists 15839 public available API (State June 2017). While ProgrammableWeb represent as set of manually collected APIs, APIHound claims to have crawled and indexed over 50000 APIs.
According to 3scale CEO Steve Willmott, eBay, Flickr, and Salesforce were among the companies that helped popularize the API \cite{tmcnet} leading towards entire business models evolving around API services and strategies. Along came new terminologies to define this industry such as API Economy and Business to Developer (B2D).

API Economy is defined as the positive affect APIs can have on an organization’s profitability.\cite{mulesoft}
It can be loosely compared to the prestige of patents plaques. The more holistic a company provides APIs the more developers can make use of it. Well documented API’s attracts developers to either actively consume APIs or even build their own business on top of it.

@@

Business to Developer (B2D), implies a business model, which is targeting developers as customers. With the movement of open source and cloud technologies developers rarely have to rely on in-house resources anymore. Instead of building a new project form the ground up, developers can access numerous available 3rd party libraries to reduce developing time and effort. For certain services and libraries, they are event willing to pay a premium.

With the rise of API demand and supply, the API Economy calls for a product market similar ecosystem. While human customers have various sources to evaluate a product or service (or API), currently no solutions exist which lets machines choose their own source of information or functionality. Most APIs are hardcoded into the application or software. The current digital market boasts of interconnectedness. Every product is in one way or the other connected to the internet and thus “made smart”, yet any or especially so called breaking changes to the API will require developers to update their code manually. 
For our research paper, we investigate one the basic requirements for machines to accomplish such breaking changes on their own. Our focus is on whether we can transform textual description to machine-usable structural descriptions, by using ProgrammableWeb, one of the largest API aggregation open source available.

\section{Datasets and Crawling}
%rechtsbündige grafik (habe ich jetzt erst mal rausgenommen, da es komisch aussah):
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following Sections. Section II.A describes the Linked Web API dataset and the issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and Section II.C shows an alternative way to get data from Google.

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset \cite{dojchinovskilinked} with 9.850 APIs. Besides short descriptions of the API, it inherits also semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection shows, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78 \% (Fig. 2) of the links were missing. From the remaining links only 9 \% were working. We tried to fix the rest of the links by deleting path and subdomain from the link. This slightly increased the amount of usable links. Overall the data quality which is achieved with this approach can be considered insufficient. A lot of the links do not point to the actual API description either because they are outdated or because the fixing approach just led us to a general page with often little connection to the API description.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/fig2.png}
\caption{Amount of working links in the Linked Data API Dataset}
\label{fig_sim}
\end{figure}

\subsection{Programmable Web Dataset}
Another approach to get usable data was, to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{https://scrapy.org} to crawl all the data. The API descriptions from Programmable Web have an averege length of 70 words, which we assumed to be not enough. We examined the linkts to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32 \% (Fig. 2) were not working. When we investigated the links further, we found out, that approximately 30 to 45 \% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim}
\end{figure}

\subsection{Google Crawled Dataset}
Since the links from the datasets in Section II.A and II.B were not usefull, we decided to crawl a complete new dataset from Google. We constructed a search query out of the API names with additional filters, shown in (1).
site:paypal.com “api documentation" OR “api reference” “paypal payments api”	(1)
We saved the first five results with every result being in its own key-value pair, so that we can distinguish between the ranks of the results. Our assumption was, that Google will return the best result (link to the actual API documentation website) on rank 1. We investigated a couple of those links and came to conclusion, that our assumption was false. Therefore we could not use the dataset from Google.
We decided to use the Programmable Web dataset with the limited amount of API descriptions.

@@

\subsection{Vectorization}
After the data cleaning, we are left with API descriptions, referenced as documents, which consist of a varying number of words, referenced as terms. Before clustering algorithms can be applied on the data it has to be transformed. The aim is to generate a matrix where every row represents an document and each column a term. The values of that matrix determine if a term is part of a description and which importance the term has. To archive this, we used the term frequency times inverse document frequency (TF-IDF) Vectorizer from the Python library scikitLearn \cite{scikit-learn}. The Vectorizer counts the frequency of a word in an API description and the frequency of that word in the whole data set. The importance of a Word then is calculated by the following formula.

\begin{equation*}
tfidf (d,t) = tf(t) * idf(d,t) 
\end{equation*}

tf(t) is the term frequency of a term in an API description. This term frequency is multiplied with the inverse document frequency which is calculated according to the following formula.

\begin{equation*}
idf (d,t) = log\left( \frac{1+n}{1+df(d,t)} \right)
\end{equation*}

N is the total number of API descriptions and df(d,t) the document frequency, the number of documents in which a term t appears. 
With the TF-IDF Vectorizer terms with a high term frequency but a low document frequency have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a spars matrix with \textcolor{red} {XXXXXXX} dimensions.

\subsection{Latent Semantic Analysis}
A dimension reduction was not only necessary because of the size of the Matrix, but is also suggested by Ding and He 2004 \cite{ding2004k}. They showed, that a dimension reduction with the Principal Component Analysis (PCA) before the use of K-Means leads to better clustering  results. Having a huge sparse matrix makes it difficult to perform a PCA. Therefore, we used the transformer TruncatedSVD from the scikitLearn library to perform a dimension reduction \cite{scikit-learn}. The transformer uses a truncated Singular Value Decomposition (SVD) which is specially tailored to TF-IDF matrixes and therefore called Latent Semantic Analysis. This makes a centering of the data not necessary and is for that reason suitable for large sparse data sets \cite{albright2004taming}.

\section{Manual Clustering}
To be able to assess the quality of our trained clusters, we decided to manually create clusters and only evaluate (in Section V) on those manually clustered APIs. With that, we could test different clustering parameters described in Section IV and choose the best parameters. We split the dataset according to the existing categories and took the five tags: “Messaging”, “Payments”, “eCommerce”, “Mapping” and “Finance”, since they contained most of the APIs. Based on the descriptions we clustered those APIs manually, so that we receive about 30 APIs per cluster. After 2-3 days of processing, we had 26 manually created clusters with 962 APIs.

\section{Clustering}
To suggest for a given API from a user similar APIs we tried two different approaches. In our first approach we used clustering algorithms which are mostly used for data mining and knowledge discovery, data compression and pattern recognition. Mostly the field of clustering algorithms for pattern recognition were capable to solve our given problem. In our case the algorithms assigned APIs to the same cluster if they had similar wording patterns and descriptions. 
Our other approach was to create a correlation matrix which declares for each API how similar it is to a given API. To achieve this the algorithm had to calculate the distance between each API and create a square matrix for the given data.
To implement and test these approaches we used the following algorithms.

\subsection{API Clustering}
For the correlation matrix we tried to implement the algorithm introduced by Jian Wu, Liang Chen, Zibin Zheng, Michael R. Lyu and Zhaohui Wu in their Paper “Clustering Web services to facilitate service discovery” \cite{kanungo2002efficient}. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn.

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE \begin{equation*}{Sim}_{con}\left(s_1,s_2\right)=\frac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{1-NGD(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|} \end{equation*}
 \STATE Add ${Sim}_{con}\left(s_1,s_2\right)$ to the correlation matrix 
\ENDFOR
\ENDFOR
\RETURN correlation matrix

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN\cite{kanungo2002efficient} is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense (minPts) and a maximum distance between two neighbours in a cluster $(\epsilon)$.

\begin{algorithm}[H]
 \caption{Algorithm 2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, \newline maximum distance between two
neighbours in a cluster, \newline word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE 
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

The main advantage of DBSCAN is that APIs without any similar APIs in a given distance, also called noise, will be ignored an assigned to a separate cluster. This results in an undistorted result and as an information for a user that there is no similar API. 
Another advantage is that there is no fixed number of clusters because this will be optimized during the execution of the algorithm.
The decisive disadvantage is that only the distance between two neighbours in a cluster are considered in the algorithm. Resulting in an unknown width of the clusters. This means that two completely different APIs could end up in the same cluster because there is a linking chain of APIs between them. With this problem there was no assurance that the algorithm produces a logical result for our use-case.
Another problem occurred during the execution of our implementation. Given a set of 3000 APIs, number of neighbours required for a API to be consider dense of minPts = 2 and a ε = 1,2 our algorithm considered half of these APIs noise and the other half was put into clusters with an average number of seven APIs. The input can be interpreted that there only must be one other API in a distance of 1,2 around a given API. This means our input had to be very vague for any results. Because of this and the wrong assignment of APIs to the noise category we did not use DBSCAN for further implementation.

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is k-means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space Rn and an integer k the algorithm determines k points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the k-means adaptation of the Lloyed-algorithm described in Algorithm 3\cite{kanungo2002efficient}.

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, \newline word-vectors of the APIs $W={w_1, w_1, ... w_n}$
 \ENSURE  k centres, affiliation of the APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE Repeat \newline
\noindent\hspace*{5mm}%		    
			Assign each item $w_i$ to the cluster which has \newline 
\noindent\hspace*{5mm}%
			the closest cetroid;\newline
\noindent\hspace*{5mm}%
			Calculate new mean for each cluster;\newline
	Until convergence criteria is met.
\RETURN centres, affiliation of the APIs
 \end{algorithmic}
 \end{algorithm}

The main advantage is the simplicity of the algorithm and performance. Another advantage is that because of the minimization of the mean square distance of the APIs to their centres we also minimize the distance between two APIs in the same cluster.
The main challenge of the k-means algorithm is that the integer k is fixed and can’t be optimized with the algorithm itself. To counteract this problem we split the possible number of clusters into intervals. For each interval we executed the k-means algorithm for the boarder points of the interval and compared the result of these outputs in our evaluation.
A problem that we couldn’t overcome was the inclusion of noise in our results. APIs without any similar APIs were still included in a cluster and this could distort our results.
Since we used k-means for our final implementation the results of this algorithm will be evaluated in the Evaluation.

\section{Evaluation}
K-Means in combination with LSA leaves us with three parameters that have to be determined, the cluster size, the distance metric, and the number of dimensions the input data was reduced to. To determine the best values for those parameters we run the clustering with different parameter combinations. The clusters resulting from the different combinations were then compared to the manually formed clusters. We used two different methods to determine the quality of the machine created clusters, the Jaccard coefficient together with the Rand Statistic and Precision and Recall. As a last step we selected one of the best parameter combinations to manually evaluate the correctness of the clustering. The following paragraph introduces the two different quality measurements and the process of the manual evaluation.

\subsection{Jaccard Coefficient}
As [Halkidi, 2002] \cite{halkidi2002cluster}  suggests we used Jaccard-Coefficient for quality measurement. Jaccard measures the intersection of two quantities. In our case on quantity is the manual created cluster, lets name it C, the other one is the cluster set that k-means provides, lets name it K. In formal:

\begin{equation*}
manual~Cluster~C := \{ c_1,c_2,...,c_n \}
\end{equation*}
\begin{equation*}
k-means~Cluster~K := \{ k_1,k_2,...,k_n \}
\end{equation*}

We used the approach for calculating Jaccard as described in [Halkidi, 2002]. Therefore, we build every possible pair Y in C.

\begin{equation*}
Y= ( y_1,y_2) : y_1, y_2 \in C
\end{equation*}

Furthermore, we search for Y in K. 
\begin{equation*}
\Rightarrow ~try~to~find:
\end{equation*}
\begin{equation*}
X= ( x_1,x_2) : x_1= y_1,x_2= y_2 \in K
\end{equation*}

Now we can derive for every possible X and Y whether $y_1$  and $y_2$ are in the same cluster and if $x_1$  and $x_2$ are in the same cluster. We can get the following combinations: \\
\begin{labeling}{Different-Diffr. (DD)}
\item [Same-same (SS)]  $i.e.~y_1,y_2 \in c_l; x_1,x_2 \in k_h$ \\
\item [Same-Different (SD)]  $i.e.~ y_1,y_2 \in c_l; x_1 \in k_h; x_2 \notin k_h$ \\
\item [Different-Same (DS)]  $i.e.~ y_1 \in c_l; y_2 \notin c_l; x_1,x_2 \in k_h$ \\
\item [Different-Diffr. (DD)]  $i.e.~y_1 \in c_l; y_2 \notin c_l; x_1 \in k_h;x_2 \notin k_h$
\end{labeling}

We count how many SS, SD, DS and DD pairs exists. With these numbers, we can calculate the Jaccard Coefficient. We also provide Rand statistics because we can easily calculate it from the same numbers.

>>>>

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}

@@

\author{Selcuk~Aklanoglu,
        Han~Che,
        Caroline~Dieterich,
        Marcel~Ruoff,
        Jan-Peter~Schmidt  \\
Karlsruhe Institute of Technology \\
Sebastian~Bader \\
Department Applied Informatics and  Formal Description Methods (AIFB)  \\
Karlsruhe Institute of Technology

@@

\begin{abstract}
In this study, we investigate the possibility of using Knowledge Discovery and Data Mining approaches to transform human written textual Web Application Programming Interface
(API) descriptions into structural descriptions, which
can be consumed by machines. The central vision
is to provide a solution, which ultimately allows
machines to interchange APIs with similar purposes
automatically. A use case would be to replace non-
responding data providing API (e.g. weather,
location, news) with another. Using descriptions
provided by ProgrammableWeb, with over 15000
APIs one of the most prominent public API library,
we conducted multiple steps of data cleaning and
preprocessing followed by machine learning
algorithms (K-Means, DBSCAN) to create clusters,
which we validated manually. With an average of only
68,3 words per descriptions (45,6 after
preprocessing), we found that the amount of clusters are between 300 and 700 unique clusters. After social-tagging activities on the prototype-website\footnote{http://webapi.bplaced.net/} for about 300 APIs, we receive a quality score of 60~\%, which means, that more than half of the APIs are probably clustered correctly. But our results suggests, that the
needed quantity for text mining and clustering was insufficiently met. Our clusters were thus also inconclusive. 
The complete code is available on github\footnote{https://github.com/Cuky88/APICrawler}.
\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{A}{pplication} Programming Interfaces (API) are not just a way to give developers access to software or services anymore. A whole business economy has established around the concept of exposing APIs in order to provide access and services. Programmable Web currently lists 15839 public available API (State June 2017). While Programmable Web represent as set of manually collected APIs, APIHound claims to have crawled and indexed over 50000 APIs.
According to 3scale CEO Steve Willmott, eBay, Flickr, and Salesforce were among the companies that helped popularize the API \cite{tmcnet} leading towards entire business models evolving around API services and strategies. Along came new terminologies to define this industry such as API Economy and Business to Developer (B2D).

API Economy is defined as the positive affect APIs can have on an organization’s profitability \cite{mulesoft}.
It can be loosely compared to the prestige of patents plaques. The more holistic a company provides APIs the more developers can make use of it. Well documented APIs attract developers to either actively consume APIs or even build their own business on top of it.

@@

Business to Developer (B2D) (Fig. \ref{fig_sim}), implies a business model, which is targeting developers as customers. With the movement of open source and cloud technologies developers rarely have to rely on in-house resources anymore. Instead of building a new project form the ground up, developers can access numerous available 3rd party libraries to reduce developing time and effort. For certain services and libraries, they are even willing to pay a premium.

With the rise of API demand and supply, the API Economy calls for a product market similar ecosystem. While human customers have various sources to evaluate a product or service (or API), currently no solutions exist, which lets machines choose their own source of information or functionality. Most APIs are hardcoded into the application or software. The current digital market boasts of interconnectedness. Every product is in one way or the other connected to the internet and thus “made smart”, yet any or especially so called breaking changes to the API will require developers to update their code manually. 
For our research paper, we investigate on the basic requirements for machines to accomplish such breaking changes on their own. Our focus is on whether we can transform textual description to machine-usable structural descriptions, by using Programmable Web, one of the largest API aggregation open source available.

\section{Datasets and Crawling}
%rechtsbündige grafik (habe ich jetzt erst mal rausgenommen, da es komisch aussah):
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following sections. Section II.A describes the Linked Web API dataset and its issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and section II.C shows an alternative way to get data from Google.

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset \cite{dojchinovskilinked} with 9.850 APIs. Besides short descriptions of the API, it inherits semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection showed, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API to get more textual descriptions. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78~\% (Fig. \ref{fig_sim2}) of the links were missing. From the remaining links only 9~\% were working. We tried to fix the rest of the links by deleting path and subdomain from the link. This slightly increased the amount of usable links. Overall the data quality which is achieved with this approach can be considered insufficient. A lot of the links do not point to the actual API description either because they are outdated or because the fixing approach just led us to a general page with often little connection to the API description.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/fig2.png}
\caption{Amount of working links in the Linked Web API Dataset}
\label{fig_sim2}
\end{figure}

\subsection{Programmable Web Dataset}
Another approach to get usable data was to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{https://scrapy.org} to crawl all the data. The API descriptions from Programmable Web have an averege length of about 70 words, which we assumed to be not enough. We examined the links to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32~\% (Fig.  \ref{fig_sim3}) were not working. When we investigated the links deeper, we found out, that approximately 30 to 45~\% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim3}
\end{figure}

\subsection{Google Crawled Dataset}
Since the links from the datasets in section II.A and II.B were not usefull, we decided to crawl a complete new dataset from Google. We constructed a search query out of the API names with additional filters, like:\\

\begin{quote}
site:paypal.com "api documentation" OR "api reference" "paypal payments api"\\
\end{quote}

We saved the first five results with every result being in its own key-value pair, so that we can distinguish between the ranks of the results. Our assumption was, that Google will return the best result (link to the actual API documentation website) on rank 1. We investigated a couple of those links and came to the conclusion, that our assumption was false. Therefore we could not use the dataset from Google.
We decided to use the Programmable Web dataset with the limited amount of API descriptions.

@@

\subsection{Vectorization}
After the data cleaning, we are left with API descriptions, referenced as documents, which consist of a varying number of words, referenced as terms. Before clustering algorithms can be applied on the data it has to be transformed. The goal here is to generate a matrix where every row represents a document and each column a term. The values of that matrix determine if a term is part of a description and which importance the term has. To archive this, we used the term frequency times inverse document frequency (TF-IDF) Vectorizer from the Python library scikitLearn \cite{scikit-learn}. The Vectorizer counts the frequency of a word in an API description and the frequency of that word in the whole data set. The importance of a word then is calculated by (\ref{eq:tdf}).

\begin{equation}
\label{eq:tdf}
tfidf (d,t) = tf(t) * idf(d,t) 
\end{equation}

tf(t) is the term frequency of a term in an API description. This term frequency is multiplied with the inverse document frequency which is calculated according to (\ref{eq:idf}).

\begin{equation}
\label{eq:idf}
idf (d,t) = log\left( \frac{1+n}{1+df(d,t)} \right)
\end{equation}

$n$ is the total number of API descriptions and $df(d,t)$ the document frequency, the number of documents in which a term $t$ appears. 
With the TF-IDF Vectorizer, terms with a high term frequency but a low document frequency, have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a sparse matrix with \textcolor{red} {XXXXXXX} dimensions.

\subsection{Latent Semantic Analysis}
A dimension reduction was not only necessary because of the size of the matrix, but is also suggested by \cite{ding2004k}. They showed, that a dimension reduction with the Principal Component Analysis (PCA) before the use of K-Means leads to better clustering  results. Having a huge sparse matrix makes it difficult to perform a PCA. Therefore, we used the transformer TruncatedSVD from the scikitLearn library to perform a dimension reduction \cite{scikit-learn}. The transformer uses a truncated Singular Value Decomposition (SVD) which is specially tailored to TF-IDF matrixes and therefore called "Latent Semantic Analysis". This makes a centering of the data unnecessary and is for that reason suitable for large sparse datasets \cite{albright2004taming}.

\section{Manual Clustering}
To be able to assess the quality of our trained clusters, we decided to manually create clusters and only evaluate (section \ref{sec:clustering}) on those manually clustered APIs. With that, we could test different clustering parameters and choose the best parameter combinations. We split the dataset according to the existing categories and took the five tags: “Messaging”, “Payments”, “eCommerce”, “Mapping” and “Finance”, since they contained most of the APIs. Based on the descriptions we clustered those APIs manually, so that we receive about 30 APIs per cluster. After 2-3 days of processing, we had 26 manually created clusters with 962 APIs.

\section{Clustering}
\label{sec:clustering}
To suggest for a given API from a user similar APIs we tried two different approaches. In our first approach we used clustering algorithms which are mostly used for data mining and knowledge discovery, data compression and pattern recognition. Mostly the field of clustering algorithms for pattern recognition were capable to solve our given problem. In our case the algorithms assigned APIs to the same cluster if they had similar wording patterns and descriptions. 
Our other approach was to create a correlation matrix which declares for each API how similar it is to a given API. To achieve this the algorithm had to calculate the distance between each API and create a square matrix for the given data.
To implement and test these approaches we used the algorithms described in the following subsections.

\subsection{Normalized Google Distance}
For the correlation matrix we tried to implement the algorithm introduced by Jian Wu, Liang Chen, Zibin Zheng, Michael R. Lyu and Zhaohui Wu in their Paper “Clustering Web services to facilitate service discovery” \cite{kanungo2002efficient}. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn (Algorithm \ref{alg:algo1}).

\begin{algorithm}[H]
 \caption{Normalized Google Distance}
 \label{alg:algo1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE 
\parbox[c][1cm]{1\linewidth}{
$Sim_{con}(s_1,s_2)=$
}
\parbox[c][1cm]{1\linewidth}{
$\dfrac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{1-NGD(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|}$
}

 \STATE Add ${Sim}_{con}\left(s_1,s_2\right)$ to the correlation matrix 
\ENDFOR
\ENDFOR
\RETURN correlation matrix

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN\cite{kanungo2002efficient} is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense ($minPts$) and a maximum distance between two neighbours in a cluster $(\epsilon)$ (Algorithm \ref{alg:algo2}).

\begin{algorithm}[H]
 \caption{Density-Based Clustering}
 \label{alg:algo2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, \newline maximum distance between two
neighbours in a cluster, \newline word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure}:
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE

%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

The main advantage of DBSCAN is that APIs without any similar APIs in a given distance, also called noise, will be ignored and assigned to a separate cluster. This results in an undistorted result and as an information for an user that there is no similar API. 
Another advantage is that there is no fixed number of clusters because this will be optimized during the execution of the algorithm.
The decisive disadvantage is that only the distance between two neighbours in a cluster are considered in the algorithm. Resulting in an unknown width of the clusters. This means that two completely different APIs could end up in the same cluster because there is a linking chain of APIs between them. With this problem there was no assurance that the algorithm produces a logical result for our use-case.
Another problem occurred during the execution of our implementation. Given a set of 3000 APIs, number of neighbours required for a API to be consider dense of $minPts = 2$ and a $ε = 1,2$ our algorithm considered half of these APIs noise and the other half was put into clusters with an average number of seven APIs. The input can be interpreted that there have to be one other API in a distance of 1,2 around a given API. This means our input had to be very vague for any results. Because of this and the wrong assignment of APIs to the noise category we did not use DBSCAN for further implementation.

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is K-Means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space R\textsuperscript{n} and an integer $k$ the algorithm determines $k$ points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the K-Means adaptation of the Lloyed-algorithm described in Algorithm \ref{Algorithm 3}\cite{kanungo2002efficient}.

\begin{algorithm}[H]
 \caption{K-Means Algorithm}
 \label{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, \newline word-vectors of the APIs $W={w_1, w_1, ... w_n}$
 \ENSURE  k centres, affiliation of the APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE Repeat \newline
\noindent\hspace*{5mm}%		    
			Assign each item $w_i$ to the cluster which has \newline 
\noindent\hspace*{5mm}%
			the closest cetroid;\newline
\noindent\hspace*{5mm}%
			Calculate new mean for each cluster;\newline
	Until convergence criteria is met.
\RETURN centres, affiliation of the APIs
 \end{algorithmic}
 \end{algorithm}

The main advantage is the simplicity of the algorithm and performance. Another advantage is that because of the minimization of the mean square distance of the APIs to their centres we also minimize the distance between two APIs in the same cluster.
The main challenge of the K-Means algorithm is that the integer $k$ is fixed and can’t be optimized with the algorithm itself. To counteract this problem we split the possible number of clusters into intervals. For each interval we executed the K-Means algorithm for the boarder points of the interval and compared the result of these outputs in our evaluation.
A problem that we couldn’t overcome was the inclusion of noise in our results. APIs without any similar APIs were still included in a cluster and this could distort our results.
Since we used K-Means for our final implementation the results of this algorithm will be evaluated in the Evaluation in section \ref{sec:eval}.

\section{Evaluation}
\label{sec:eval}
K-Means in combination with LSA leaves us with three parameters that have to be determined, the cluster size, the distance metric, and the number of dimensions the input data was reduced to. To determine the best values for those parameters we run the clustering with different parameter combinations. The clusters resulting from the different combinations were then compared to the manually formed clusters. We used two different methods to determine the quality of the machine created clusters, the Jaccard-Coefficient together with the Rand Statistic and Precision and Recall. As a last step we selected one of the best parameter combinations to manually evaluate the correctness of the clustering. The following paragraph introduces the two different quality measurements and the process of the manual evaluation.

\subsection{Jaccard Coefficient}
As \cite{halkidi2002cluster} suggests we used Jaccard-Coefficient for quality measurement. Jaccard measures the intersection of two quantities. In our case one quantity are the manual created clusters, lets name it $C$, the other one are the cluster sets that K-Means provides, lets name it $K$. Formally described in equation (\ref{eq:manClus}) and (\ref{eq:kmeanClus}):

\begin{equation}
\label{eq:manClus}
manual~Cluster~C := \{ c_1,c_2,...,c_n \}
\end{equation}
\begin{equation}
\label{eq:kmeanClus}
k-means~Cluster~K := \{ k_1,k_2,...,k_n \}
\end{equation}

We used the approach for calculating Jaccard as described in \cite{halkidi2002cluster}. Therefore, we build every possible pair $Y$ in $C$ (\ref{eq:yinc}).

\begin{equation}
\label{eq:yinc}
Y= ( y_1,y_2) : y_1, y_2 \in C
\end{equation}

Furthermore, we search for $Y$ in $K$ (\ref{eq:yink}). 
\begin{equation*}
\Rightarrow ~try~to~find:
\end{equation*}
\begin{equation}
\label{eq:yink}
X= ( x_1,x_2) : x_1= y_1,x_2= y_2 \in K
\end{equation}

Now we can derive for every possible $X$ and $Y$ whether $y_1$  and $y_2$ are in the same cluster and if $x_1$  and $x_2$ are in the same cluster. We can get the following combinations: \\
\begin{labeling}{Different-Diffr. (DD)}
\item [Same-Same (SS)]  $i.e.~y_1,y_2 \in c_l; x_1,x_2 \in k_h$ \\
\item [Same-Different (SD)]  $i.e.~ y_1,y_2 \in c_l; x_1 \in k_h; x_2 \notin k_h$ \\
\item [Different-Same (DS)]  $i.e.~ y_1 \in c_l; y_2 \notin c_l; x_1,x_2 \in k_h$ \\
\item [Different-Diffr. (DD)]  $i.e.~y_1 \in c_l; y_2 \notin c_l; x_1 \in k_h;x_2 \notin k_h$\\
\end{labeling}

We count how many SS, SD, DS and DD pairs exists. With these numbers, we can calculate the Jaccard-Coefficient (\ref{eq:jacc}). We also provide Rand Statistics (\ref{eq:rand}), which can be easily calculated from the same numbers.
